### 2020-06-05 report/sections/introduction/contributions.tex
Report: minor structural changes

In \cref{chap:theory}, we introduce a variant of multiparty 
session type theory with routing. We prove that our extensions preserve 
properties required for communication safety, 
session fidelity and deadlock freedom.
We provide an encoding for global types into routed multiparty 
session type theory, and prove the preservation of well-formedness
and communication. Detailed lemmas and proofs in this section can
be found in \cref{appendix:proofs}.

@@

This project was published as \emph{Generating Interactive WebSocket 
Applications in TypeScript} in the Proceedings of the 
12th International Workshop on Programming Language Approaches to 
Concurrency- \& Communication-cEntric Software (PLACES 2020) 
\cite{PLACES2020}.

>>>>

In \cref{chap:theory}, we introduce a variant of multiparty 
session type theory with routing. We prove that our extensions preserve 
properties required for communication safety, 
session fidelity and deadlock freedom.
We provide an encoding for global types into routed multiparty 
session type theory, and prove the preservation of well-formedness
and communication. Detailed lemmas and proofs in this section can
be found in \cref{section:proofs}.

@@

\begin{remark}
This project was published as \emph{Generating Interactive WebSocket 
Applications in TypeScript} in the Proceedings of the 
12th International Workshop on Programming Language Approaches to 
Concurrency- \& Communication-cEntric Software (PLACES 2020) 
\cite{PLACES2020}.
\end{remark}
